ESBMC-GPU \\ A Context-Bounded Model Checking Tool \\ to Verify CUDA Programs

### 2017-05-15 Publications/Original Software Publications/Science of Computer Programming/source/manuscript.tex
updating Funtionalities section
Signed-off-by: Felipe R. Monteiro <rms.felipe@gmail.com>

Through the integration of COM into ESBMC ({\it i.e.}, ESBMC-GPU), one is able to analyze CUDA programs and verify the following properties: data-race conditions, in order to detect if multiple threads perform unsynchronized access \textcolor{blue}{to the same memory locations}; pointer safety, {\it i.e.}, whether {\it (i)} a pointer offset does not exceed object bounds and {\it (ii)} a pointer is neither {\tt NULL} nor invalid; array bounds, in order to ensure that array indices are within known bounds; arithmetic under- and overflow, which happens when a sum or product exceeds the memory limits that a variable can handle; division by zero, which takes place when denominators, in arithmetic expressions, lead to a division by zero; and user-specified assertions, {\it i.e.}, all assertions specified by users, which is essential to a thorough verification process.%, as some specific possible violations must be explicitly pointed out.

In order to check the aforementioned properties, ESBMC-GPU explicitly explores the possible interleavings (up to the given context bound) and calls the single-threaded BMC procedure on each one, whenever it reaches an RT leaf node. Then, the mentioned procedure will stop if it finds a bug or when all possible RT interleavings \textcolor{blue}{have been systematically explored}~\cite{pereira:2016}.

>>>>

%Through the integration of COM into ESBMC ({\it i.e.}, ESBMC-GPU), one is able to analyze CUDA programs and verify the following properties: data-race conditions, in order to detect if multiple threads perform unsynchronized access \textcolor{blue}{to the same memory locations}; pointer safety, {\it i.e.}, whether {\it (i)} a pointer offset does not exceed object bounds and {\it (ii)} a pointer is neither {\tt NULL} nor invalid; array bounds, in order to ensure that array indices are within known bounds; arithmetic under- and overflow, which happens when a sum or product exceeds the memory limits that a variable can handle; division by zero, which takes place when denominators, in arithmetic expressions, lead to a division by zero; and user-specified assertions, {\it i.e.}, all assertions specified by users, which is essential to a thorough verification process.%, as some specific possible violations must be explicitly pointed out.

%In order to check the aforementioned properties, ESBMC-GPU explicitly explores the possible interleavings (up to the given context bound) and calls the single-threaded BMC procedure on each one, whenever it reaches an RT leaf node. Then, the mentioned procedure will stop if it finds a bug or when all possible RT interleavings \textcolor{blue}{have been systematically explored}~\cite{pereira:2016}.

\textcolor{blue}{Through the integration of COM into ESBMC ({\it i.e.}, ESBMC-GPU), one is able to analyze CUDA programs and verify the following properties:}

\begin{itemize}
	\item[--] \textcolor{blue}{\textbf{Data race.} ESBMC-GPU checks data race conditions, in order to detect if multiple threads perform unsynchronized access \textcolor{blue}{to the same memory locations};}

	\item[--] \textcolor{blue}{\textbf{Pointer safety.} ESBMC-GPU also ensures that {\it (i)} a pointer offset does not exceed object bounds and {\it (ii)} a pointer is neither {\tt NULL} nor invalid;}

	\item[--] \textcolor{blue}{\textbf{Array bounds.} ESBMC-GPU performs array-bound checking, in order to ensure that any variable, used as an array index, is within known bounds;}

	\item[--] \textcolor{blue}{\textbf{Arithmetic under- and overflow.} ESBMC-GPU checks whether a sum or product exceeds the memory limits that a variable can handle, which can cause an error capable of spreading through the entire execution path;}

	\item[--] \textcolor{blue}{\textbf{Division by zero.} ESBMC-GPU analyzes whether denominators, in arithmetic expressions, lead to a division by zero;}

	\item[--] \textcolor{blue}{\textbf{User-specified assertions.\ } ESBMC-GPU considers all assertions specified by users, which is essential to a thorough verification process, as some specific possible violations must be explicitly pointed out.}
\end{itemize}

In order to check the aforementioned properties, ESBMC-GPU explicitly explores the possible interleavings (up to the given context bound) and calls the single-threaded BMC procedure on each one, whenever it reaches an RT leaf node. Then, the mentioned procedure will stop if it finds a bug or when all possible RT interleavings \textcolor{blue}{have been systematically explored}~\cite{pereira:2016}. \textcolor{blue}{Furthermore, ESBMC-GPU has the following additional command-line options:
\\
\texttt{--no-assertions}: to ignore assertions; \\
\texttt{--no-bounds-check}: to skip array bounds check; \\
\texttt{--no-div-by-zero-check}: to skip division by zero check; \\
\texttt{--no-pointer-check}: to skip pointer check; \\
\texttt{--memory-leak-check}: to enable memory leak check; \\
\texttt{--overflow-check}: to enable arithmetic over- and underflow check; \\
\texttt{--deadlock-check}: to enable global and local deadlock check with mutex; \\
\texttt{--data-races-check}: to enable data races check; \\
\texttt{--lock-order-check}: to enable for lock acquisition ordering check; \\
\texttt{--atomicity-check}: to enable atomicity check at visible assignments; \\
\texttt{--memlimit}: to configure memory limit, of form ``100MB'' or ``2GB''; \\
\texttt{--timeout}: to configure time limit, integer followed by \{s, m, or h\}; \\
\texttt{--force-malloc-success}: to consider that there is always enough memory available in the device; \\
\texttt{-DGPU\_threads=<$number$>}: to define the total number of threads by kernel. \\}
